---
title: "R Notebook"
output: html_notebook
---

```{r setup}
knitr::opts_chunk$set(message = FALSE)
```

From Julia Silge's video: https://www.youtube.com/watch?v=EDQnJF9LKHQ
About this TidyTuesday dataset

Decision tree model for predicting capacity of wind turbines based on their characteristics, location, and year of commissioning. Visualization with some other packages:`parttree`, `vip`


```{r}
library(tidyverse)
library(tidymodels)
library(skimr)
theme_set(theme_minimal())
```


```{r}
turbines <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-10-27/wind-turbine.csv')
skimr::skim(turbines)

```
### Tidy data

```{r}
turbine_df <- turbines %>% 
  transmute(
    turbine_capacity = turbine_rated_capacity_k_w,
    rotor_diameter_m,
    hub_height_m,
    longitude, 
    latitude,
    # fix some year labels 
    commissioning_date = parse_number(commissioning_date),
    # lump some rare factors together, keep top 10
    model = fct_lump_n(model, n = 10),
    province_territory = fct_lump_n(province_territory, 8)
    ) %>% 
  filter(!is.na(turbine_capacity)) %>% 
  mutate_if(is.character, factor)

skimr::skim(turbine_df)
```

## Turbine capacity against predictors
```{r}

turbine_df %>% 
  pivot_longer(rotor_diameter_m:commissioning_date) %>% 
  ggplot(aes(turbine_capacity, value)) +
  geom_hex(alpha = 0.8, bins =15) +
  geom_smooth(method = 'lm') +
  facet_wrap(~name, scales = 'free_y') +
  labs(y = 'null') +
  scale_fill_viridis_c() 
```

### Split data

```{r}
# split data
set.seed(123)
wind_split <- initial_split(turbine_df)
wind_split
wind_train <- training(wind_split)
wind_test <- testing(wind_split)

# create folds to pass for resampling
set.seed(234)
wind_folds <- vfold_cv(wind_train)
wind_folds
```

### Set up model tuning search

```{r}
# an rpart decision tree regression model
# we'll search for cost, depth, min 
tree_spec <- decision_tree(
  cost_complexity = tune(), 
  tree_depth = tune(), 
  min_n = tune()
  ) %>% 
  set_engine("rpart") %>% 
  set_mode("regression")

tree_spec

# set up the grid to search over
tree_grid <- grid_regular(cost_complexity(), min_n(), tree_depth(),
                          levels = 4)
tree_grid

doParallel::registerDoParallel()
set.seed(345)

# do hyperparameter tuning with: model, formula/recipe, cv, grid
tree_rs <- tune_grid(
  object = tree_spec, 
  turbine_capacity ~ .,
  resamples = wind_folds,
  grid = tree_grid,
  metrics = metric_set(rmse, rsq, mae, mape)
)

```

### Explore Tuning Results

```{r}
autoplot(tree_rs) + theme_light()
```


```{r}
collect_metrics(tree_rs)
show_best(tree_rs, 'rmse')
# best model
select_best(tree_rs, 'rmse')

```

### Final tree, not fit yet

```{r}
# finalize best model and train on all training data
final_tree <- finalize_model(tree_spec, select_best(tree_rs, 'rmse'))
final_fit <- fit(final_tree, turbine_capacity ~ ., wind_train)

# final_fit # contains the rpart tree model, can see partitions
```

### Predicting test data

```{r}
# alternately, use last_fit
final_rs <- last_fit(final_tree, turbine_capacity~., wind_split)
final_rs
```


```{r}
# eg.
# predict(final_fit, wind_train)
```

### Variable importance

```{r}
library(vip)
final_fit %>% 
  vip(geom ='col', aesthetics = list(fill = 'midnightblue', alpha = 0.8)) +
  scale_y_continuous(expand = c(0,0))
```

## Visualize partioning

```{r}
# can only have two predictors for this visualization
example_fit <- fit(final_tree, 
                   turbine_capacity ~ rotor_diameter_m + commissioning_date,
                   wind_train)

# remotes::install_github("grantmcdermott/parttree")
library(parttree)

wind_train %>% 
  ggplot(aes(rotor_diameter_m, commissioning_date, color = turbine_capacity)) +
  geom_parttree(data = example_fit, 
                aes(fill=turbine_capacity),
                alpha = 0.4, color = 'white', size = 0.5) +
  geom_jitter(width = 0.8, alpha = 0.5, height = 0.5) +
  scale_colour_viridis_c(aesthetics = c('color','fill'))
```


### Visualize prediction accuracy

```{r}
collect_predictions(final_rs) %>% 
  ggplot(aes(turbine_capacity, .pred)) +
  geom_point(alpha = 0.6, size = 0.7) + 
  geom_abline(slope = 1, lty = 2, alpha = 0.8, color = 'gray') +
  coord_equal()
  
```

```{r}

```

