---
title: "CEO departures bootstrap model"
date: "`r Sys.Date()`"
output:
  rmdformats::downcute:
    self_contained: true
---


```{r setup, include=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```


## dataset description

`read_lines("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-04-27/readme.md")`

Departure codes indicate reason for replacement (3 and 4 are fired; NA is still employed).

```{r data}
library(tidyverse)
library(broom)
library(rsample)

departures <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-04-27/departures.csv")

glimpse(departures)
```


```{r filter}
departures <- departures %>% 
  filter(departure_code < 9)
```


```{r plot_ts}
departures %>% 
  filter(fyear > 1995 & fyear < 2019) %>% 
  mutate(involuntary = if_else(departure_code %in% 3:4, 'fired', 'other')) %>% 
  count(involuntary, fyear) %>% 
  ggplot(aes(fyear, n, color = involuntary)) +
  geom_line() +
  geom_smooth(method = 'lm', lty=2) +
  scale_y_continuous(limits = c(0,NA))
  
```


## Bootstrapping a model

A model to measure whether the proportion of CEOs leaving involuntarily is statistically significant. GLM binomial model with successes/failures, where successes are involuntary departures. Can we explain the proportion with the year?

```{r filter2}
departures <- departures %>% 
  filter(fyear > 1995 & fyear < 2019) %>% 
  mutate(involuntary = if_else(departure_code %in% 3:4, 'involuntary', 'other'))

# format counts data by year
df <- departures %>% 
  count(fyear, involuntary) %>% 
  pivot_wider(names_from = involuntary, values_from = n)
df


mod <- glm(cbind(involuntary, other) ~ fyear, 
           data = df, family = 'binomial')
tidy(mod, exponentiate = TRUE)
```

```{r bootstraps}
set.seed(123)
ceo_folds <- bootstraps(departures, times = 1e3)
```

A function to get the coefficients of linear model for a bootstrapping sample.
```{r fit_model}
fit_binom <- function(split) {
  # format counts data by year
  df <- 
    analysis(split) %>% 
    count(fyear, involuntary) %>% 
    pivot_wider(names_from = involuntary, values_from = n)
  # fit model
  mod <- glm(cbind(involuntary, other) ~ fyear, 
             data = df, family = 'binomial')
  # return model data
  tidy(mod, exponentiate = TRUE)
}
```

Get summaries of 1000 models
```{r fit_all_models}
boot_models <- ceo_folds %>% 
  mutate(coef_info = map(splits, fit_binom))
```

Get bootstrapped confidence intervals from 1000 models
```{r CIs}
intervals <- int_pctl(boot_models, coef_info)
intervals
```

## Results

There is a ~1.5% increase in the likelihood of a CEO departure being involuntary (fired) per year.

```{r }
boot_models %>%
  unnest(coef_info) %>% 
  filter(term == 'fyear') %>% 
  ggplot(aes(estimate)) + 
  geom_vline(aes(xintercept = 1), lty = 2) +
  geom_histogram(fill = 'midnightblue')
```


